# A few summary stats from ESA 2012


<!-- read external r code -->
```{r reading, echo=FALSE}
read_chunk("tweet_stats.R")
opts_knit$set(base.url='https://raw.github.com/karthikram/esa_twitter_impact/master/')
opts_chunk$set(fig.width=6, fig.height=5)
```

## Cumulative Exposure of ESA 2012 tweets
The cumulative number of impressions that tweets tagged esa2012 recevied since the last week of July until now.

```{r plot-fig0, result="asis", echo = FALSE}
<<cumplot>>
```

## Total ESA2012 tweets
Ecologists tweeted ~4905 times from the last week of July to one week after the conference. Most number of tweets in a single day was Wednesday the 7th quite likely coinciding with Carly Strasser's very popular session.

```{r plot-fig0a, result="asis", echo = FALSE}
<<totalplot>>
```

## Tweets by sentiment (blue = positive, red = negative)
Tweets were categorized as positive or negative based on a standard set of keywords. 

```{r plot-fig3, result="asis", echo = FALSE}
<<splot>>
```

## Mentions of ESA2012 over time scaled by impact
Tweets on a hourly timescale. High impact tweets are ones that were retweeted and favorited more than others. The lulls during the week correspond to night time hours.

```{r plot-fig1, result="asis", echo = FALSE}
<<aplot>>
```
## Tweets by country
These are tweets and retweets by country. Not surprisingly most tweets originated from Portland but American ecologists also retweeted the most followed by the UK and Canada.

```{r plot-fig2, result="asis", echo = FALSE}
<<geoplot>>
```
## Popular tags associated with ESA 2012
These are tags that popped up as being popular alongside the esa2012 tag. Not sure why middleagedwhitedude and hawaiianshirt trended so much.


```{r plot-fig4, result="asis", echo = FALSE}
<<dplot>>
```
 

