<!-- read external r code -->
```{r reading, echo=FALSE}
read_chunk("tweet_stats.R")
opts_knit$set(base.url='/Users/karthik/Dropbox/esa_twitter_impact/')
opts_chunk$set(fig.width=8, fig.height=6)
```

# Early Draft title: Social media interactions increase the impact of large scientific conferences and faciliate rapid collaborations.

__Karthik Ram__ and __Christopher J. Lortie__


__Introduction__


__Methods__

__A data analysis section of some sort__


# Summary stats from the esa2012 tweets
These are some summaries on tweets tagged `#esa2012` between mid-July and mid-August. There were approximately 4905 tweets about the conference (still waiting on the raw data) but I was able to scrape some analytics data from the [Topsy API](http://code.google.com/p/otterapi/). I have additional information on the most popular links, photos and videos from the conference but have not summarized those. 

Please note that these results aren't ready to be shared yet (barely scratched the surface) but do watch the repository for updates.


## Cumulative Exposure of ESA 2012 tweets
The cumulative number of impressions that tweets tagged `#esa2012` received between mid-July and now.

```{r data, result="asis", echo = FALSE}
<<cum_exposure>>
```

```{r plot-fig0, result="asis", echo = FALSE}
<<cumplot>>
```


__Literature Cited__
