<!-- read external r code -->
```{r reading, echo=FALSE}
read_chunk("~/Dropbox/esa_twitter_impact/tweet_stats.R")
opts_knit$set(base.url='https://raw.github.com/karthikram/esa_twitter_impact/master/')
opts_chunk$set(fig.width=8, fig.height=6)
```

# Summary stats from the esa2012 tweets
These are some summaries on tweets tagged `#esa2012` between mid-July and mid-August. There were approximately 4905 tweets about the conference (still waiting on the raw data) but I was able to scrape some analytics data from the [Topsy API](http://code.google.com/p/otterapi/). I have additional information on the most popular links, photos and videos from the conference but have not summarized those. 

Please note that these results aren't ready to be shared yet (barely scratched the surface) but do watch the repository for updates.


## Cumulative Exposure of ESA 2012 tweets
The cumulative number of impressions that tweets tagged `#esa2012` received between mid-July and now.

```{r plot-fig0, result="asis", echo = FALSE}
<<cumplot>>
```

## Total ESA2012 tweets
Ecologists tweeted ~4905 times from the last week of July to one week after the conference. Most number of tweets in a single day was Wednesday the 7th quite likely coinciding with Carly Strasser's very popular session.

```{r plot-fig0a, result="asis", echo = FALSE}
<<totalplot>>
```

## Tweets by sentiment (blue = positive, red = negative)
Tweets were categorized as positive or negative based on a standard set of keywords. 

```{r plot-fig3, result="asis", echo = FALSE}
<<splot>>
```

## Mentions of ESA2012 over time scaled by impact
Tweets on a hourly timescale. High impact tweets are ones that were retweeted and favorited more than others. The lulls during the week correspond to night time hours.

```{r plot-fig1, result="asis", echo = FALSE}
<<aplot>>
```
## Tweets by country
These are tweets and retweets by country. Not surprisingly most tweets originated from Portland but American ecologists also retweeted the most followed by the UK and Canada.

```{r plot-fig2, result="asis", echo = FALSE}
<<geoplot>>
```
## Popular tags associated with ESA 2012
These are tags that popped up as being popular alongside the esa2012 tag. Not sure why middleagedwhitedude and hawaiianshirt trended so much.


```{r plot-fig4, result="asis", echo = FALSE}
<<dplot>>
```
## R 
R got mentioned consistently throughout the week and most on Thursday (when [rOpenSci](http://ropensci.org) held its workshop.) 

```{r plot-fig5, result="asis", echo = FALSE}
<<rstats>>
```
 
## ESA Social 
ESA Social also got most mentions on the day of the social media workshop (Tuesday)

```{r plot-fig6, result="asis", echo = FALSE}
<<esasocial>>
```
 

